Making Sequential Programs Deterministic

### 2019-03-27 experiments.tex
expts

P1 :
[ERROR] /Users/rashmi/caseStudies/nondex/reflectasm/src/com/esotericsoftware/reflectasm/FieldAccess.java:[102,87] [assignment.type.incompatible] incompatible types in assignment.
[ERROR]   found   : @Det Field @OrderNonDet []
[ERROR]   required: @Det Field @Det []

P2:

		if (object instanceof Map) {
    emitter.emit(new MappingStartEvent(anchor, tag, !showTag, false));
    @Det Set<@Det Object> items = ((Map)object).entrySet();
    @Det Iterator<@Det Object> itemIterator = items.iterator();
    while (itemIterator.hasNext()) {
        Object item = itemIterator.next();
        Entry entry = (Entry)item;
        writeValue(entry.getKey(), null, null, null);
        if (isRoot && !config.writeConfig.writeRootElementTags) elementType = entry.getValue().getClass();
        writeValue(entry.getValue(), elementType, null, null);
    }
    //			for (@Det Object item : ((Map)object).entrySet()) {
        //				Entry entry = (Entry)item;
        //				writeValue(entry.getKey(), null, null, null);
        //				if (isRoot && !config.writeConfig.writeRootElementTags) elementType = entry.getValue().getClass();
        //				writeValue(entry.getValue(), elementType, null, null);
        //			}
    emitter.emit(Event.MAPPING_END);
    return;
}

>>>>

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Benchmark & Recall? & Error message source & # annotations & Type of annotation added & Comments \\ \hline
        P1 &  &  &  &  &  \\
        P2 &  &  &  &  &  \\
        P3 &  &  &  &  &  \\ 
        P4 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\ 
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P9 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P11 &  &  &  &  &  \\
        P12 &  &  &  &  &  \\
        P13 &  &  &  &  &  \\
        P14 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P16 &  &  &  &  &  \\
        P17 &  &  &  &  &  \\
        P18 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\ \hline
    \end{tabular}
\end{table}
